Towards Verifying the Bitcoin-S Library

### 2019-06-28 paper/paper.tex
fix
add information about sbt/JAR

@@

Stainless does not currently support a class with a type parameter
with a type boundary that contains the class itself. We opened an
issue \cite{Stainless:issue519} on the Stainless repository and the
Stainless developers have targeted Stainless version 0.4 to support
such self-referential type boundaries.

>>>>

\todo{
Kai:

sbt-plugin vs JAR:
Can use either sbt-plugin or JAR

More about sbt on https://www.scala-sbt.org/1.x/docs/index.html (features are also listed there)
Installation see Stainless Doc 'Installing Stainless' section

Use JAR:
Download all library dependencies including dependencies of dependencies, pass libraries + source to JAR

Use sbt-plugin: integrate in sbt build tool with addSbtPlugin() method

Why JAR:
sbt-plugin problems (v 0.1 uses older versions (v0.2 not), no output to console see github \#484)
otherwise use sbt-plugin because of library management and replicability (everyone uses the same Stainless version configured in sbt)

Reproduce results:
prereq: Java 8 in /usr/lib/jvm/java-8-openjdk
1. clone repo
2. run ./code/bin/stainless.sh <path to code>
   eg. ./code/bin/stainless.sh code/addition/src/main/scala/addition/reduced/
}

@@

Stainless does not currently support a class with a type parameter
with a type boundary that contains the type parameter itself. We opened an
issue \cite{Stainless:issue519} on the Stainless repository and the
Stainless developers have targeted Stainless version 0.4 to support
such self-referential type boundaries.
